### 2017-02-26 2017mergingmerges/section/03-Definition.tex
S3: Copy edits to injection

% -----------------------------------------------------------------------------
\eject{}
\subsubsection{Injection}
Fig.~\ref{fig:Process:Eval:Inject} gives the rules for injecting values into processes. The judgment form $\ProcInject{p}{v}{c}{p'}$ reads ``given process $p$, injecting value $v$ into channel $c$ yields a new process $p'$''. The @injects@ form is similar, but for sets of processes rather than a single one.

Rule (InjectValue) handles the injection of a single value into a single process.

% Injection is used by the other parts of evaluation to \emph{inject} stream values into a process' input buffer.

A process has a single element buffer for each input, stored in its input state.
This can be either @none@, in which case the buffer is empty and a value may be injected; @pending@, where a single value has been injected to the buffer but has not been pulled yet; or @have@, where a value has already been injected and is currently being used.

% Injection is only possible when the process' input buffer is empty, or the process ignores that stream. Injection for a process network proceeds by injecting the same value into all processes in the network.

Rule (InjectValue) allows a value to be injected only when the input state is @none@, meaning the buffer is empty.
An attempt to inject a value while the buffer is @pending@ or @have@ would require an unbounded, or at least multiple element, buffer.
We use the syntax ($\HeapUpdateOne{@ins@~p}{c}{@pending@~v}$) to perform a map update, in this case removing the ($c=@none@$) from ($@ins@~p$) and then inserting ($c=@pending@~v$).
This sets the input buffer as pending, meaning that any future attempts to inject to this channel will fail, until the process pulls and then drops the value.

Rule (InjectIgnore) allows processes that do not use a particular input stream to ignore an injected input.

Rule (ProcessesInject) performs injection over a process network.
Every process in the network must have the value injected into it.
This means if multiple processes read from that stream, all input buffers for that stream must be empty.

% Injecting requires the input buffer to be empty or the process to ignore that channel.
For networks, all processes must successfully inject the value.

>>>>

% -----------------------------------------------------------------------------
\eject{}
\subsubsection{Injection}
Fig.~\ref{fig:Process:Eval:Inject} gives the rules for injecting values into processes. The judgment form $\ProcInject{p}{v}{c}{p'}$ reads ``given process $p$, injecting value $v$ into channel $c$ yields a new process $p'$''. The @injects@ form is similar, but operates on sets of processes rather than a single one.

Rule (InjectValue) injects of a single value into a single process. The value is stored as a (@pending@~ v) binding in the $\InputState$ for the associated channel of the process. The $\InputState$ acts as a single element buffer, and must be empty (set to @none@) for the injection to succeed.

Rule (InjectIgnore) allows processes that do not use a particular named channel to ignore values injected into that channel.

Rule (InjectMany) attempts to inject a single value into a set of processes. We use the single process judgment form to inject the value into all processes in the set, which must succeed for all of the. Once a value has been injected into all consuming processes that require it, it is then safe for a producing process to discard it.
